## Appendix B: Otthers Accuracy Test Results

Where `Total Rows` means the number of the input data rows.
`Given # Clusters` means the number of clusters as one of the given parameters.
`Result # Clusters` means the number of clusters  as a result of the clustering.
`Dimension` means the number of dimensions of the input data vector.
`Train Times` means the execution time as milliseconds to train the model.
`Predict Time` means the execution time as milliseconds to predict with the data.
`Squared Mean Variance` means the squared value of the mean variance for all result clusters.

`Count` at `Result Vectors and Their Rows` means the nuber of vectors in each cluster.
`Variance` at `Result Vectors and Their Rows` means the sum of the variances for all dimension of each cluster.
`Vector` at `Result Vectors and Their Rows` means the head three element of the center of each cluster. In short, it is good that the vector is nearly equal to its seed vector.

`Count` at `Seed Vectors and Their Rows` means the number of generated vectors of each cluster.
`Seed Vector` at `Seed Vectors and Their Rows` means the head three elements of the seed vector of each cluster.

### The Number of Dimensions: 5 

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-5.txt',
              'data/accuracy-test/accuracy-test-10-5.txt',
              'data/accuracy-test/accuracy-test-20-5.txt',
              'data/accuracy-test/accuracy-test-50-5.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 10

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-10.txt',
              'data/accuracy-test/accuracy-test-10-10.txt',
              'data/accuracy-test/accuracy-test-20-10.txt',
              'data/accuracy-test/accuracy-test-50-10.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 20

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-20.txt',
              'data/accuracy-test/accuracy-test-10-20.txt',
              'data/accuracy-test/accuracy-test-20-20.txt',
              'data/accuracy-test/accuracy-test-50-20.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 50

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-50.txt',
              'data/accuracy-test/accuracy-test-10-50.txt',
              'data/accuracy-test/accuracy-test-20-50.txt',
              'data/accuracy-test/accuracy-test-50-50.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 100

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-100.txt',
              'data/accuracy-test/accuracy-test-10-100.txt',
              'data/accuracy-test/accuracy-test-20-100.txt',
              'data/accuracy-test/accuracy-test-50-100.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 200

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-200.txt',
              'data/accuracy-test/accuracy-test-10-200.txt',
              'data/accuracy-test/accuracy-test-20-200.txt',
              'data/accuracy-test/accuracy-test-50-200.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```

### The Number of Dimensions: 1000

```{r echo=FALSE, warning=FALSE, comment=""}
files <- c(
              'data/accuracy-test/accuracy-test-5-1000.txt',
              'data/accuracy-test/accuracy-test-10-1000.txt',
              'data/accuracy-test/accuracy-test-20-1000.txt',
              'data/accuracy-test/accuracy-test-50-1000.txt'
           )
for (i in 1:length(files)) {
  .file <- file(description = files[i], open = "r")
  print(readLines(.file))
  close(.file)
}
```
