## Experiment 2: Slaves x 5

### EC2 Environment

I run the hierarchical clustering application on EC2. 

- Master Instance Type: r3.large
- Slave Instance Type: r3.8xlarge
    - Cores: 32
    - Memory: 144GB
- # of Slaves: 5
    - Total Cores: 64
    - Total Memory: 239GB

### Experimental Setup

I execute my hierarchical clustering, changing the some parameters as bellow.  The data had been generated randomly. And then I measured the execution time for training each model.

- # Used Cores: 160
- # Clusters: 5, 10, 20, 50, 100
- # Rows: 100000, 500000, 1000000, 5000000, 10000000
- # Dimensions: 100

### The Result of Training Execution Time

```{r echo=FALSE, warning=FALSE}
library(reshape2)
result2 <- read.csv("./data/benchmark-cores64-dim100-slave5.csv")
result2$sec <- result2$trainMilliSec / 1000
```

```{r echo=FALSE, warning=FALSE}
result2.cast <- dcast(result2, numClusters ~ rows, value.var="sec", sum)
x <- result2.cast[, 1]
y <- result2.cast[, 2:6]
matplot(x, y
        , xlab="# Clusters"
        , ylab="Training Execution Time [sec]"
        , pch=1:(length(y)), col=rainbow(length(y)), type="o")
grid()
legend("topleft", legend=c(names(y))
       , pch=1:(length(y)), col=rainbow(length(y)))
```

```{r echo=FALSE, warning=FALSE}
result2.cast <- dcast(result2, rows ~ numClusters, value.var="sec", sum)
x <- result2.cast[, 1]
y <- result2.cast[, 2:6]
matplot(x, y
        , xlab="# Rows"
        , ylab="Training Execution Time [sec]"
        , pch=1:(length(y)), col=rainbow(length(y)), type="o")
grid()
legend("topleft", legend=c(names(y))
       , pch=1:(length(y)), col=rainbow(length(y)))
```

```{r echo=FALSE, warning=FALSE, results="asis"}
kable(result2)
```
Where `maxCores` is the number of execution cores on Apache Spark,`numClusters` is the number of clusters gotten, `trainMilliSec` is the execution time for training in millisecond, `dimension` is the number of dimensions of the vectors which are treated in the clustering algorithm, `rows` is the number of trained vectors, `numPartitions` is the number of partitions of a RDD, `sec` is the execution time for training in second.
