## Experiment 3: About cores

- Object: Check the efficient of the number of cores

### EC2 Environment

I run the hierarchical clustering application on EC2. 

- Master Instance Type: r3.large
- Slave Instance Type: r3.8xlarge
    - Cores: 32
    - Memory: 144GB
- # of Slaves: 5
    - Total Cores: 160
    - Total Memory: 1220GB

### Experimental Setup

I execute my hierarchical clustering, changing the some parameters as bellow.  The data had been generated randomly. And then I measured the execution time for training each model.

- # Used Cores(# Slaves: 5): 2, 4, 6, 8, 10, 12, 14, 16, 18, 20
- # Clusters: 10
- # Rows: 200000
- # Dimensions: 100

### The Result of Training Execution Time

```{r echo=FALSE, warning=FALSE}
library(reshape2)
result3 <- read.csv("./data/benchmark-dim100.csv")
result3$sec <- result3$trainMilliSec / 1000
```

```{r echo=FALSE, warning=FALSE}
result3.cast <- dcast(result3, maxCores ~ rows, value.var="sec", sum)
x <- result3.cast[, 1]
y <- result3.cast[, 2:4]
matplot(x, y
        , xlab="# Cores"
        , ylab="Training Execution Time [sec]"
        , ylim=c(0, max(y))
        , pch=1:(length(y)), col=rainbow(length(y)), type="o")
grid()
legend("topright", legend=c(colnames(y))
       , pch=1:(length(y)), col=rainbow(length(y)))
```

```{r echo=FALSE, warning=FALSE, results="asis"}
kable(result3)
```

Where `maxCores` is the number of execution cores on Apache Spark,`numClusters` is the number of clusters gotten, `trainMilliSec` is the execution time for training in millisecond, `dimension` is the number of dimensions of the vectors which are treated in the clustering algorithm, `rows` is the number of trained vectors, `numPartitions` is the number of partitions of a RDD, `sec` is the execution time for training in second.


```{r echo=FALSE, warning=FALSE}
x <- result3.cast[, 1]
y <- apply(result3.cast[, 2:4], 2, function(x) {x / x[1]})
matplot(x, y
        , xlab="# Cores"
        , ylab="Index against # CPU Cores:2"
        , ylim=c(0, max(y))
        , pch=1:(ncol(y)), col=rainbow(ncol(y)), type="o")
grid()
legend("topright", legend=c(colnames(y))
       , pch=1:(ncol(y)), col=rainbow(ncol(y)))
```

```{r echo=FALSE, warning=FALSE, results="asis"}
result3.cast.index <- cbind(x, y)
kable(result3.cast.index)
```
